\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
Re-organisation of results and discussion

We had two measures of performance. First measure was a rating given to
the responses that participants gave to the question about the
functionality of the robot. Second measure was the distance from the
target in the interaction phase.

We transcribed the responses to perform a rating scheme on the level of
abstraction and correctness. A low level of abstraction consists in
describing the functionality of the robot in the terms of the electric
or programming aspects of the robot, a high level represents describing
the behaviour. For the levels of correctness, we categorised the
responses into correct or incorrect response. In TABLE I. we present
sample responses for the different categories.

\begin{table}[ht!]
    \centering
    \footnotesize
    \begin{tabular}{ccp{4.5cm}}
        \toprule
        Correct. & Abstract. & Sample answer \\
        \midrule
        \textit{incorrect} & \textit{low} & ``The robot turns at a given distance in respect to a colour, defined in the program.''\\ 
        \midrule
        \textit{incorrect} & \textit{high} & `Grey is the most dangerous, so the
        robot turn really early.''\\ 
        \midrule
        \textit{correct} & \textit{low} & ``The grey obstacle reflects a lot,
        the robot sends light. At a certain threshold the robot turns.'' \\ 
        \midrule
        \textit{correct} & \textit{high} & ``The grey obstacle is shinier, so
        more reflective, and better detectable.''\\ 
        \bottomrule
    \end{tabular}
    \caption{Sample answers for all classes}

    \label{sample_answer}
\end{table}

Second, the distances from the target were measured for all 5 trials. As
a matter of fact, as soon as the principle of the robot was deemed to be
understood by the participants, almost all the participants behaved the
same way. On the first try almost every participant failed and the robot
turned instantly. So the most significant distance measure was the
improvement between the first and second trial. It is referred to as
improvement in the following sections.

Incorrect answers were further classified into 4 categories; we present
each category accompanied by a sample response:

\begin{itemize}
    \item The participant did not respond or offer a possible explanation: ``I
        really don't know how the robot works''.

    \item The participant identified a wrong cause for the behaviour of the robot:
        ``The robot notices the tags on the side''.

    \item The participant held the code responsible for the cause of different
        behaviour: ``The robot turns at a given distance in respect to a color,
        defined in the program''.

    \item The participant tried to explain by analogies or did not explain the
        robots behaviour at an understandable level: ``Grey is the most
        dangerous, so the robot turns really early''.

\end{itemize}

@@

\section{Discussion}

We present an eye-tracking study in the context of human-robot
interaction with an educational setting. The fact that participants have
higher average fixation duration on the robot during the observation
phase in the {\sf NONE} condition than the other two conditions (Figure 4) is
not surprising as displaying visual information on the robot induces a
saliency effect on the attention and the gaze is attracted towards the
salient feature in the field of view.

@@

The fact that participants have lower average fixation duration on the
reference side in the interaction phase in the {\sf TRUE} condition than the
other two conditions actually supports the explanation that participants
with {\sf TRUE} condition had a higher initial belief in their cognitive model
of how does the robot work (Figure 6). They did not need to look onto
the reference given in observation phase. This also verifies our working
hypothesis that a carefully designed mapping between the robot's
behavior and its visual actuators can help in maximising the learning
effect during the interaction.

Another plausible explanation for the participants in {\sf NONE} and {\sf RANDOM} condition
being better performers than the {\sf TRUE} condition during the interaction phase
comes from the transparency of the robot's behaviour. The robot's
behaviour was not at all transparent in the former two conditions. This might
have caused the participants to put more effort in understanding the behaviour.
Therefore, they performed better.

@@

We addressed two research questions in the beginning of the present
work. The results show that the way the sensor data is visualised has an
impact on both the gaze patterns and the performance (Question 2).
However, for the relation between the gaze patterns of the participants
and their performance outcomes (Question 1) we cannot claim a direct
relation. We found a negative correlation between the gaze-patterns and
the first improvement during the interaction phase. We could not find a
relation between the explanation of the participants and their
gaze-patterns. Moreover, we did not find any anticipation patterns in
the gaze data. The lack of evidence for the relation between
participants' explanations and their gaze patterns prevents us to make
any strong claims about the relation between the overall performance and
the gaze patterns.

The fact that we cannot find a relation between the gaze patterns and
all the factors in the performance might have its roots in the way we
designed the interaction phase experiment. As a working hypothesis we
said that there should be clear and carefully designed mapping between
the robots' behaviour and the sensor data visualization. Its environment
also affects the behaviour of the robot and hence the environment also
should be taken into consideration while designing the
behavior-visualisation mapping. We introduced a novelty (the gray
obstacle being more reflective) in the environment during the
interaction phase of the experiment that forced the participants to
revise their hypothesis and hence they failed to understand the robot's
functionality. This also serves as a word of caution in future while
designing such interactions. The observation phase serves as a training
session for the participants, which can later be tested during the
interaction phase. Any novel behaviour modality (in our case, the more
reflective grey obstacle) can have a negative impact on the
participants' understanding.

>>>>

%We had two measures of performance. First measure was a rating given to
%the responses that participants gave to the question about the
%functionality of the robot. Second measure was the distance from the
%target in the interaction phase.

%We transcribed the responses to perform a rating scheme on the level of
%abstraction and correctness. A low level of abstraction consists in
%describing the functionality of the robot in the terms of the electric
%or programming aspects of the robot, a high level represents describing
%the behaviour. For the levels of correctness, we categorised the
%responses into correct or incorrect response. In TABLE I. we present
%sample responses for the different categories.

%\begin{table}[ht!]
%    \centering
%    \footnotesize
%    \begin{tabular}{ccp{4.5cm}}
%        \toprule
%        Correct. & Abstract. & Sample answer \\
%        \midrule
%        \textit{incorrect} & \textit{low} & ``The robot turns at a given distance in respect to a colour, defined in the program.''\\ 
%        \midrule
%        \textit{incorrect} & \textit{high} & `Grey is the most dangerous, so the
%        robot turn really early.''\\ 
%        \midrule
%        \textit{correct} & \textit{low} & ``The grey obstacle reflects a lot,
%        the robot sends light. At a certain threshold the robot turns.'' \\ 
%        \midrule
%        \textit{correct} & \textit{high} & ``The grey obstacle is shinier, so
%        more reflective, and better detectable.''\\ 
%        \bottomrule
%    \end{tabular}
%    \caption{Sample answers for all classes}
%
%    \label{sample_answer}
%\end{table}

We measured the distances from the target were measured for all 5 trials. As
a matter of fact, as soon as the principle of the robot was deemed to be
understood by the participants, almost all the participants behaved the
same way. On the first try almost every participant failed and the robot
turned instantly. So the most significant distance measure was the
improvement between the first and second trial. It is referred to as
improvement in the following sections.

%Incorrect answers were further classified into 4 categories; we present
%each category accompanied by a sample response:
%
%\begin{itemize}
%    \item The participant did not respond or offer a possible explanation: ``I
%        really don't know how the robot works''.
%
%    \item The participant identified a wrong cause for the behaviour of the robot:
%        ``The robot notices the tags on the side''.
%
%    \item The participant held the code responsible for the cause of different
%        behaviour: ``The robot turns at a given distance in respect to a color,
%        defined in the program''.
%
%    \item The participant tried to explain by analogies or did not explain the
%        robots behaviour at an understandable level: ``Grey is the most
%        dangerous, so the robot turns really early''.
%
%\end{itemize}

@@

\section{Interpreting the results}

We present an exemplar eye-tracking study in the context of human-robot
interaction within an educational setting. In this section we give an example of "how to interpret the eye-tracking results". The fact that participants have higher average fixation duration on the robot during the observation phase in the {\sf NONE} condition than the other two conditions (Figure 4) is not surprising as displaying visual information on the robot induces a saliency effect on the attention and the gaze is attracted towards the salient feature in the field of view.

The fact that the participants in the {\sf RANDOM} or {\sf NONE} visualisation condition improved more than those with {\sf TRUE} condition is surprising (Figure 5). There are two plausible explanations. The first is that participants who see the robot in the {\sf TRUE} condition have a stronger belief that the robot always behaves the same. They see the LEDs of the robot turning on and therefore the robot still works. The ones with {\sf NONE} visualisation do not have an indication whether the robot works the same way as in the observation phase, and start experimenting earlier. The second explanation is that the participants in {\sf TRUE} condition just put the obstacles out of detection range, because they could see different display information and concluded therefore it may behave differently.

@@

The fact that participants have lower average fixation duration on the
reference side in the interaction phase in the {\sf TRUE} condition than the
other two conditions actually supports the explanation that participants
with {\sf TRUE} condition had a higher initial belief in their cognitive model
of how does the robot work (Figure 6). They did not need to look onto
the reference given in observation phase. This also verifies our working
hypothesis that a carefully designed mapping between the robot's
behaviour and its visual actuators can help in maximising the learning
effect during the interaction.

%Another plausible explanation for the participants in {\sf NONE} and {\sf RANDOM} condition
%being better performers than the {\sf TRUE} condition during the interaction phase
%comes from the transparency of the robot's behaviour. The robot's
%behaviour was not at all transparent in the former two conditions. This might
%have caused the participants to put more effort in understanding the behaviour.
%Therefore, they performed better.
\section{Discussion}

@@

%We addressed two research questions in the beginning of the present
%work. The results show that the way the sensor data is visualised has an
%impact on both the gaze patterns and the performance (Question 2).
%However, for the relation between the gaze patterns of the participants
%and their performance outcomes (Question 1) we cannot claim a direct
%relation. We found a negative correlation between the gaze-patterns and
%the first improvement during the interaction phase. We could not find a
%relation between the explanation of the participants and their
%gaze-patterns. Moreover, we did not find any anticipation patterns in
%the gaze data. The lack of evidence for the relation between
%participants' explanations and their gaze patterns prevents us to make
%any strong claims about the relation between the overall performance and
%the gaze patterns.
%
%The fact that we cannot find a relation between the gaze patterns and
%all the factors in the performance might have its roots in the way we
%designed the interaction phase experiment. As a working hypothesis we
%said that there should be clear and carefully designed mapping between
%the robots' behaviour and the sensor data visualization. Its environment
%also affects the behaviour of the robot and hence the environment also
%should be taken into consideration while designing the
%behavior-visualisation mapping. We introduced a novelty (the gray
%obstacle being more reflective) in the environment during the
%interaction phase of the experiment that forced the participants to
%revise their hypothesis and hence they failed to understand the robot's
%functionality. This also serves as a word of caution in future while
%designing such interactions. The observation phase serves as a training
%session for the participants, which can later be tested during the
%interaction phase. Any novel behaviour modality (in our case, the more
%reflective grey obstacle) can have a negative impact on the
%participants' understanding.
